Selecting the Maximum-Utility Web Services Using Circuits

### 2009-12-16 publicaciones/eswc10/paperESWC10.tex
parte de experimental results rellena

  \documentclass{llncs}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage[boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{enumerate}
\DeclareGraphicsExtensions{.jpg, .png, .mps, .bmp, .pdf}
\usepackage{epsfig}
\usepackage{subfigure}
\newtheorem{Definition}{Definition} 
\newtheorem{Example}{Example} 
\newtheorem{Theorem}{Theorem} 
\newtheorem{Proof}{Proof} 
\newcommand{\denselist}{\topsep 0pt \itemsep -4pt}
\newcommand{\tup}[1]{\langle #1 \rangle}
\newcommand{\vvec}[1]{\mathbf{#1}}
\newcommand{\join}{\bowtie}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\body}{{body}}
\newcommand{\head}{{head}}
\newcommand{\qrule}{:\!\!-}
\newcommand{\arc}{\text{arc}}
\newcommand{\Theory}[1]{T(#1)}
\newcommand{\mcdsat}{\textsc{McdSat}}
\newcommand{\minicon}{{MiniCon}}
\newcommand{\Omit}[1]{}
\newcommand{\citeX}[1]{\citeauthor{#1}~\citeyear{#1}}

@@

\section{Experimental Results}
We have conducted an empirical analysis  on the benefits of the techniques implemented in the  {\it SsdSat} system.

\begin{description}
\item[Dataset and Query Benchmark:]  we conducted our experiments over a benchmark that includes XX queries and a set of  YY views. Queries and views are starts and chains, and they have between ZZ and TT constants; queries have QQ sub-subgoals.
\item[Evaluation Metrics:] we report on runtime performance which corresponds to the  {\it user time} produced by the {\it time} command of the Unix operation system. 
\end{description}

@@

>>>>

\documentclass{llncs}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage[boxed]{algorithm2e}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{enumerate}
\DeclareGraphicsExtensions{.jpg, .png, .mps, .bmp, .pdf}
\usepackage{epsfig}
\usepackage{subfigure}
\newtheorem{Definition}{Definition} 
\newtheorem{Example}{Example} 
\newtheorem{Theorem}{Theorem} 
\newtheorem{Proof}{Proof} 
\newcommand{\denselist}{\topsep 0pt \itemsep -4pt}
\newcommand{\tup}[1]{\langle #1 \rangle}
\newcommand{\vvec}[1]{\mathbf{#1}}
\newcommand{\join}{\bowtie}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\body}{{body}}
\newcommand{\head}{{head}}
\newcommand{\qrule}{:\!\!-}
\newcommand{\arc}{\text{arc}}
\newcommand{\Theory}[1]{T(#1)}
\newcommand{\mcdsat}{\textsc{McdSat}}
\newcommand{\ssdsat}{{\it SsdSat} }
\newcommand{\minicon}{{MiniCon}}
\newcommand{\Omit}[1]{}
\newcommand{\citeX}[1]{\citeauthor{#1}~\citeyear{#1}}

@@

\section{Experimental Results}
We have conducted an empirical analysis on the benefits of the techniques
implemented in the  {\it SsdSat} system. The characteristics of the experiment
follow:

\begin{description}
\item[Dataset and Query Benchmark:] we evaluated the system on a set of three
different benchmarks as described below. The objective was to assess the
performance of \ssdsat on varying conditions.
\item[Tests:] A benefit of the \ssdsat approach is that one can compile the
logical theory of a given problem instance and then calculate all rewritings or
the best ones any number of times in linear time. The cost model for finding
best rewritings can even be changed with no need to recompile the logical
theory, which is the costly phase of the process. Because of this, for each run
benchmark we make a clear distinction on whether the reported times comprise
theory compilation only or compilation plus enumeration rewriting.
\item[Evaluation Metrics:] we report on runtime performance which corresponds to the {\it user time} produced by the {\it time} command of the Unix operating system. 
\item[Environment:] the experiments were run on a machine with an Intel Core 2 Duo 2GHz processor and 4GB of RAM.
\end{description}

The first benchmark consisted of a problem instance modeled on air
travel queries. Concrete services were of the form

\begin{alignat*}{1}
v_i(\vvec{x}, \vvec{y})\ \qrule\ \  flight(\vvec{x},\vvec{y},i)
\end{alignat*}

Here, we suppose a service returns all flights between two cities with a specific
airline. View $i$ describes flights for the airline $i$, since the abstract service
$flight(x,y,a)$ is satisfied when a direct flight exists departing from city $x$
and arriving at city $y$ with airline $a$. Workflows had the form

\begin{alignat*}{1}
q(\vvec{x}_1, \ldots, \vvec{x}_n)\ \qrule\ flight(CCS, \vvec{x}_1, \vvec{a}),
flight(\vvec{x}_1, \vvec{x}_2, \vvec{a}),
\ldots,
flight(\vvec{x}_{n-1}, \vvec{x}_n, \vvec{a}),
flight(\vvec{x}_n, WAS, \vvec{a})
\end{alignat*}

Our benchmark for this type of problem included workflows with two to five
sub-goals and sets of five to eighty concrete services. We measured both compilation time
and time to list all rewritings. As it turned out, listing all rewritings took
less than half a second in the worst case. The results for compilation time can
be seen in figure \ref{fig:plot1}.

@@

In an attempt to induce exponential growth in the number of rewritings so as to
get longer rewriting generation times, we modified this benchmark setting the
number of concrete services per airline to two. We ran tests with this modification and the
same numbers of workflow sub-goals and concrete services (meaning we were now handling five to
forty airlines). For this case we recorded full rewriting enumeration times,
resulting in the graph in figure \ref{fig:plot2}.

\begin{figure}
\centering
\includegraphics[width=8cm]{plot1.pdf}
\caption{Rewriting Enumeration Time Benchmark I}
\label{fig:plot2}
\end{figure}

Although both tests previously described showed good results, they suffered from
a considerable issue which was lack of multiple sub-goals in concrete services.
We therefore began running tests with unstructured, randomly generated instances
with three variables per abstract service, ten distinct variables and ten
distinct constants, four sub-goals in workflows and concrete services and a
$50\%$ probability of constants appearing in each abstract service argument. We
can observe results in figure \ref{fig:plot3}.

\begin{figure}
\centering
\includegraphics[width=8cm]{plot1.pdf}
\caption{Compilation Time Benchmark I}
\label{fig:plot3}
\end{figure}
